ZCB Pricing

### 2018-07-24 ZCB Pricing .Rmd
Modified CN

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250==, J = seq(-0.3,0.5,0.01)){
  # I = partition of time interval
  # J = partition of short rate interval

@@

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}
plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

>>>>

CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.6,0.01)){
  # I = partition of time interval
  # J = partition of short rate interval

@@

xvec <- seq(-0.4,0.6,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}
plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```
